---
title: "InnerSource Adoption at the Organizations"
output: html_document
---

<style type="text/css">
.main-container {
  max-width: 1200px;
  margin-left: auto;
  margin-right: auto;
  font-size: 150%;
}
</style>

```{r setup, prep, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(maps)
library(hrbrthemes)
library(viridis)
library(scales)
library(stringr)
library(ggthemr)
library(RColorBrewer)
library(egg)
library(dplyr)
require(scales)
library(likert)
library(plyr)

myPalette <- brewer.pal(5, "Set2") 
ggthemr("grape") 

# For processing multiple answer data
process.mad = function(x){
  x = x[!(is.na(x))]
  x = unlist(x)
  x = paste(x,',')
  x = unlist(strsplit(x,','))
  x = trimws(x)
  x = x[x != ""]

  return(table(x))
}
process.lik = function(x){
  return(factor(x, levels = c("Strongly Disagree", "Disagree", "Neutral", "Agree", "Strongly Agree")))
}
process.lik.imp = function(x){
  return(factor(x, levels = c("Not Important", "Slightly Important", "Medium Important", "Very Important", "Critically Important")))
}





sudata = read.csv("_DONOTADD_State_of_the_InnerSource_Survey 2020_Responses.csv", na.strings = c('NA',''))
sudata$Timestamp = NULL
header.map = colnames(sudata)
names(header.map) = paste0("v",seq(79))
colnames(sudata) = paste0("v",seq(79))
sudata$v79 = NULL
sudata$v78 = NULL
sudata = data.frame(lapply(sudata, trimws))
# Shorten some Responses
sudata$v4 = gsub('Top-Down: Someone from management initiated the adoption', 'Top-Down: Initiated by Management', sudata$v4)
sudata$v4 = gsub('A mix of both', 'A Mix of Top-Down & Bottom Up', sudata$v4)
sudata$v4 = gsub('Bottom-Up: One/A small group of developers started the initiative', 'Bottom-Up: Initiated by developer(s)', sudata$v4)

sudata$v6 = gsub("Recognition that the current approach won't scale with our ambitions / trajectory.", 'Accommodate Scaling', sudata$v6)
sudata$v6 = gsub("Maintain and develop software developed by contractors that are no longer with the organization", 'Maintain Software w/o Contractor Support', sudata$v6)
sudata$v6 = gsub("Avoid wasted time/resources solving similar problems multiple times in isolation", 'Creating reusable software', sudata$v6)
sudata$v8 = gsub("We formed a cross organization group under our Open Source Program Office to foster the practice of InnerSource",'Establish InnerSource Foundation', sudata$v8)

# Specific Answer questions
toFact = c(2,4,11:15,18:40, 43:61, 70:72)
sudata[,toFact] = lapply(sudata[,toFact], as.factor)
# Numeric data
numdata = c(1,3,5,10,63,67,68,73,75,76)
for (i in numdata){
  sudata[,i] = as.numeric(gsub('[^0-9.-]','',sudata[,i]))
}
```

### *The Basics*

```{r, company.basic, echo=FALSE, fig.show="hold", out.width="50%", warning=FALSE, fig.width=7, fig.height=6}
#Team
tf = as.data.frame(table(sudata$v2))
tf$piepercent<- round(100*tf$Freq/sum(tf$Freq), 1)
pie(tf$Freq, labels = paste0(tf$piepercent,"%"), main = paste0(" Does the Organization have a \n dedicated InnerSource Team? (N=",length(na.omit(sudata$v2)),")"),col=myPalette, cex.lab=2, cex.axis=2, cex.main=1.8, cex.sub=2)
legend("bottomright",tf$Var1, cex = 1.2, fill = myPalette, legend = tf$Var1)

# Introduction
t=process.mad(sudata$v4)
df = as.data.frame(t)
df$x = as.character(levels(df$x))
df$newx = str_wrap(df$x, width = 18)
df = df[order(df$Freq, decreasing = T),]
df$piepercent<- round(100*df$Freq/length(na.omit(sudata$v4)), 0)

ggplot(data=df, aes(x = reorder(newx, Freq), y = Freq)) +
  geom_bar(position="dodge",stat="identity") + coord_flip() + 
  labs(title=str_wrap(paste0("Introduction of InnerSource N=(",length(na.omit(sudata$v4)),")"), 25), x='', y =  'No. of Respondents' ) +  scale_x_discrete(guide = guide_axis(n.dodge=2)) +theme(text = element_text(size=18)) +  geom_text(aes(label=paste0(Freq,'(',piepercent,"%)")), position=position_dodge(width=0.9), hjust = -0) + scale_y_continuous(limits = c(0,20))



#No. Projects
plt1 <- subset(sudata, !is.na(v3)) %>% select(v3) %>%
  ggplot(aes(x="", y = v3)) +
  geom_boxplot(fill = "lightblue", color = "black") +
  geom_violin(alpha = 0.2, color=myPalette[1]) +  
  scale_y_continuous(breaks=c(0,4,25,100,2000), trans = "log1p")  + 
  coord_flip() +
  xlab("") + ylab("No. of Projects Distribution") +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(), text = element_text(size=20), 
        axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1))
plt2 <- ggplot(data = subset(sudata, !is.na(v3)), aes(x=factor(v3))) +
  geom_histogram( stat = "count", color='black', alpha=0.9, position = "identity")  +
  labs(title = paste0(' No. of InnerSource Projects \n at the Organization (N=',length(na.omit(sudata$v3)),")"), x='No. of Projects', y='No. of Organizations' ) + theme(text = element_text(size=20))  + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

invisible(egg::ggarrange(plt2, plt1, heights = 2:1))

# InnerSource years
plt1 <- subset(sudata, !is.na(v5)) %>% select(v5) %>%
  ggplot(aes(x="", y = v5)) +
  geom_boxplot(fill = "lightblue", color = "black") + 
  geom_violin(alpha = 0.2, color=myPalette[1]) +
  coord_flip() + scale_y_continuous(trans = "log1p", breaks = c(0,1,2,3, 10, 20)) +
  xlab("") + ylab("InnerSource Experience Distribution") +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(), text = element_text(size=20), 
        axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1))
plt2 <- ggplot(data = subset(sudata, !is.na(v5)), aes(x=factor(v5))) +
  geom_histogram( stat = "count", color='black', alpha=0.9, position = "identity")  +
  labs(title = paste0(" Organization's InnerSource \n Experience (N = ",length(na.omit(sudata$v5)),")"), x='Years', y='No. of Organizations' ) + theme(text = element_text(size=18))  + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + scale_y_continuous(position = "right")


invisible(egg::ggarrange(plt2, plt1, heights = 2:1))

```
<br></br>

### **Adopting InnerSource and its Effects**
```{r, adopt, echo=FALSE, fig.show="hold", out.width="70%", fig.align="center", fig.height=7}
# Reason Adoption
t=process.mad(sudata$v6)
df = as.data.frame(t)
df$x = as.character(levels(df$x))
df$newx = str_wrap(df$x, width = 20)
df = df[order(df$Freq, decreasing = T),]
df$piepercent<- round(100*df$Freq/length(na.omit(sudata$v6)), 0)

ggplot(data=df, aes(x = reorder(newx, Freq), y = Freq)) +
  geom_bar(position="dodge",stat="identity") + coord_flip() + 
  labs(title=str_wrap(paste0("Reasons for InnerSource Adoption (N=",length(na.omit(sudata$v6)),")"),30), x='', y = 'No. of Responses') +  scale_x_discrete(guide = guide_axis(n.dodge=2)) +theme(text = element_text(size=13)) +  geom_text(aes(label=paste0(Freq,'(',piepercent,"%)")), position=position_dodge(width=0.9), hjust = -0) + scale_y_continuous(limits = c(0,39))

# Step Adoption
t=process.mad(sudata$v8)
df = as.data.frame(t)
df$x = as.character(levels(df$x))
df[7,1] = "Following InnerSource Patterns"
df$newx = str_wrap(df$x, width = 20)
df = df[order(df$Freq, decreasing = T),]
df$piepercent<- round(100*df$Freq/length(na.omit(sudata$v8)), 0)
ggplot(data=df, aes(x = reorder(newx, Freq), y = Freq)) +
  geom_bar(position="dodge",stat="identity") + coord_flip() + 
  labs(title=str_wrap(paste0("Steps taken to make InnerSource Successful (N=",length(na.omit(sudata$v6)),")"), 35), x='', y = 'No. of Responses') +  scale_x_discrete(guide = guide_axis(n.dodge=2)) +theme(text = element_text(size=13)) +  geom_text(aes(label=paste0(Freq,'(',piepercent,"%)")), position=position_dodge(width=0.9), hjust = -0) + scale_y_continuous(limits = c(0,25))

# Effect Adoption
t=process.mad(sudata$v7)
df = as.data.frame(t)
df$x = as.character(levels(df$x))
df$newx = str_wrap(df$x, width = 20)
df = df[order(df$Freq, decreasing = T),]
df$piepercent<- round(100*df$Freq/length(na.omit(sudata$v7)), 0)
ggplot(data=df, aes(x = reorder(newx, Freq), y = Freq)) +
  geom_bar(position="dodge",stat="identity") + coord_flip() + 
  labs(title=str_wrap(paste0("Observed Progress since InnerSource Adoption in: (N= ",length(na.omit(sudata$v6)),")"), 32), x='', y = 'No. of Responses') +  scale_x_discrete(guide = guide_axis(n.dodge=2)) +theme(text = element_text(size=13)) +  geom_text(aes(label=paste0(Freq,'(',piepercent,"%)")), position=position_dodge(width=0.9), hjust = -0) + scale_y_continuous(limits = c(0,32))

```
<br></br>

# **InnerSource Project Contributions**


```{r, fig.show="hold", warning=FALSE, echo=FALSE, out.width="70%", fig.height=7, fig.width= 8, fig.align="center"}
# Contribution
t=process.mad(sudata$v41)
df = as.data.frame(t)
df$x = as.character(levels(df$x))
df$newx = str_wrap(df$x, width = 20)
df = df[order(df$Freq, decreasing = T),]
df$piepercent<- round(100*df$Freq/length(na.omit(sudata$v41)), 0)

ggplot(data=df, aes(x = reorder(newx, Freq), y = Freq)) +
  geom_bar(position="dodge",stat="identity") + coord_flip() + 
  labs(title=str_wrap(paste0("InnerSource Project Contributions (N=",length(na.omit(sudata$v41)),")"), 25), x='', y = 'No. of Respondents') +  scale_x_discrete(guide = guide_axis(n.dodge=2)) +theme(text = element_text(size=16)) +  geom_text(aes(label=paste0(Freq,'(',piepercent,"%)")), position=position_dodge(width=0.9), hjust = -0) + scale_y_continuous(limits = c(0,34))
```
<br></br>

# **Effect of InnerSource Adoption on self**

```{r, effect, echo=FALSE, fig.show="hold", out.width="80%", fig.align="center", fig.width=12}
# self effect
lv = data.frame(lapply(sudata[,18:22], process.lik))
lik.name = unlist(lapply(header.map[18:22], FUN = function(x){
  return(trimws(gsub("\\."," ",gsub('.*\\.\\.\\.','',x))))
}))
colnames(lv) = paste0(lik.name," (N = ",colSums(!is.na(sudata[,18:22])),")")
lk = likert(lv)
plot(lk, centered=T, plot.percents =T, text.size=4, wrap=30, plot.percent.neutral=F, plot.percent.low=T, plot.percent.high=T) + theme(text = element_text(size=20)) + guides(fill=guide_legend(""))

```
<br></br>


# **InnerSource Practices at the Organization**
```{r, practices, echo=FALSE, fig.show="hold", out.width="80%", warning=FALSE, fig.align="center", fig.height=10, fig.width=12}
# practices
lv = data.frame(lapply(sudata[,27:36], process.lik))
lik.name = unlist(lapply(header.map[27:36], FUN = function(x){
  return(trimws(gsub("\\."," ",gsub('.*\\.\\.','',x))))
}))
colnames(lv) = paste0(lik.name," (N = ",colSums(!is.na(sudata[,27:36])),")")
lk = likert(lv)
plot(lk, centered=T, plot.percents =T, text.size=4, wrap=30, plot.percent.neutral=F, plot.percent.low=T, plot.percent.high=T) + theme(text = element_text(size=20)) + guides(fill=guide_legend(""))


```


<br></br>

## **Perceived Progress and Success in InnerSource Adoption**

```{r, progress-success, echo=FALSE, fig.show="hold", out.width="50%", warning=FALSE}
# Progress
ggplot(data = subset(sudata, !is.na(v1)), aes(x=factor(v1))) +
  geom_histogram( stat = "count", color='black', alpha=0.9, position = "identity")  +
  labs(title = str_wrap('Perceived Current Progress with InnerSource (on a scale of 1-5, 1 - Preparing for Adoption, 5 - InnerSource Pioneer)', 45), x='Years', y= paste0('No. of Organizations (N=',length(na.omit(sudata$v1)),")") ) + theme(text = element_text(size=16))  + scale_y_continuous(breaks = c(0,3,5,8,10,14))

# Success
ggplot(data = subset(sudata, !is.na(v10)), aes(x=factor(v10))) +
  geom_histogram( stat = "count", color='black', alpha=0.9, position = "identity")  +
  labs(title = str_wrap('Perceived Success of the InnerSource Projects (on a scale of 1-5, 1 - Not Successful, 5 - Extremely Successful)', 45), x='Years', y=paste0('No. of Organizations (N=',length(na.omit(sudata$v10)),")") ) + theme(text = element_text(size=16))  + scale_y_continuous(breaks = c(0,2,6,9,21), position = "right")

```

<br></br>

# **Measuring InnerSource Adoption Progress/Success**

### *Common Themes: * No. of InnerSource Ready projects, Cross-team Contributions, No. of Contributors, Employee Feedback/Survey

### *Full Responses:*
```{r, echo=FALSE, results="asis"}
# Like
cat((paste("* ",na.omit(sudata$v9), collapse = "\n")))

```

<br></br>

## Statistically Significant Relationships:

* Having an InnerSource team with How long ago InnerSource was introduced --- Positive correlation, p-Value: 0.017
* No. of InnerSource Projects with how long ago InnerSource was introduced --- Positive correlation, p-Value: 4.4e-07
* Perceived InnserSource Progress with having an InnerSource team --- Positive correlation, p-Value: 0.001
* Perceived InnserSource Success with having an InnerSource team --- Positive correlation, p-Value: 0.014
* Perceived InnserSource Progress with how long ago InnerSource was introduced --- Positive correlation, p-Value: 0.0005
* Perceived InnserSource Success with how long ago InnerSource was introduced --- Positive correlation, p-Value: 0.005
* Perceived InnserSource Success with Perceived InnserSource Progress --- Positive correlation, p-Value: 1e-5

<i><u>No. of InnerSource projects had no significant relationship with the perceived InnerSource progress or success !</u></i>
<br></br>
